\documentclass{e_class_article}

\title{Sample Article}
\author{Author Name}
\date{\today}

% --- Document Starts ---
\begin{document}

\maketitle

\begin{abstract}
    This is a sample abstract for the article document class. It demonstrates the basic structure and capabilities of our custom article template, including mathematical notation and custom environments.
\end{abstract}

\section{Introduction}

This document demonstrates the use of our custom article template. We can use all our predefined commands and environments. For example, we can easily write mathematical notation for the set of real numbers, $\mbbR$, or the expectation, $\mbbE$.

\begin{special_columns}{Key Features}
    This colored box highlights the key features of our article template. It provides a clean, professional layout suitable for academic papers and technical documents.
\end{special_columns}

\section{Mathematical Content}

Our template supports comprehensive mathematical typesetting:

\begin{align}
    f(x) &= \sum_{n=0}^{\infty} \frac{f^{(n)}(a)}{n!}(x-a)^n \\
    &= f(a) + f'(a)(x-a) + \frac{f''(a)}{2!}(x-a)^2 + \cdots
\end{align}

\subsection{Lists and Formatting}

Our list styles are also customized:
\begin{enumerate}
    \item First key point about the article structure.
    \item Second point demonstrating the custom numbering style.
    \item Third point showing consistency across elements.
\end{enumerate}

\section{Conclusion}

This sample demonstrates the article document class capabilities, providing a foundation for academic and professional writing with consistent styling and mathematical support.

\end{document}