\documentclass[12pt,cjk]{e_class_thesis}

\title{Sample Thesis Document}
\author{Graduate Student}
\date{\today}

% --- Document Starts ---
\begin{document}

\maketitle
\mytoc

\chapter{Introduction}

This document demonstrates the thesis document class, designed for longer academic works such as master's theses, doctoral dissertations, and comprehensive research reports. The template provides a structured framework for extensive academic writing.

\begin{special_columns}{Thesis Template Features}
    The thesis class provides comprehensive support for multi-chapter documents, including proper chapter formatting, cross-referencing, and academic citation standards.
\end{special_columns}

\section{Research Context}

Academic research requires careful presentation of complex ideas and mathematical formulations. Our template supports sophisticated typesetting for expressions like:

\begin{align}
    \mathcal{L}(\theta) &= \sum_{i=1}^{n} \log p(x_i|\theta) \\
    \hat{\theta}_{MLE} &= \arg\max_{\theta} \mathcal{L}(\theta)
\end{align}

\section{Methodology}

The methodology section demonstrates various formatting capabilities:

\subsection{Experimental Design}
\begin{enumerate}
    \item Hypothesis formulation and theoretical framework
    \item Data collection and preprocessing procedures
    \item Statistical analysis and validation methods
    \item Results interpretation and discussion
\end{enumerate}

\chapter{Literature Review}

This chapter would typically contain an extensive review of relevant literature, properly cited and organized thematically.

\section{Theoretical Foundations}

Complex mathematical derivations and proofs can be presented clearly:

$$\frac{\partial}{\partial \theta} \mathcal{L}(\theta) = \sum_{i=1}^{n} \frac{\partial}{\partial \theta} \log p(x_i|\theta) = 0$$

\section{Current Research Trends}

Modern research in this field focuses on several key areas, each requiring detailed mathematical treatment and empirical validation.

\chapter{Methodology and Results}

\section{Data Analysis}

Statistical results and their interpretation form a crucial part of thesis work. Our template ensures proper formatting for tables, figures, and mathematical expressions.

\section{Discussion}

The discussion section integrates findings with existing literature and theoretical frameworks.

\chapter{Conclusions and Future Work}

\section{Summary of Contributions}

This thesis has demonstrated several key contributions:
\begin{itemize}
    \item Novel theoretical framework development
    \item Empirical validation of proposed methods
    \item Practical applications and implementations
    \item Future research directions
\end{itemize}

\section{Future Directions}

Future research should explore extensions of this work to related domains and investigate scalability considerations for larger datasets.

% ==============================================================================
% APPENDIX
% ==============================================================================
\appendix

\input{color_appendix.tex}

\end{document}